Title

### 2024-05-11 paper/main.tex
Udpates

	Causal Discovery that is learning the causal graph from observational
	data is a fundamental problem in causal inference. The problem has been
	extensively studied and many algorithms have been developed to address
	it. However, their adaption in applied fields have been limited,
	possibly due to a lack of confidence in these algorithms stemming from
	them making obvious mistakes, and the difficulties in choosing the
	right algorithm for specific datasets. Moreover, these algorithms can
	usuallly only get us to markov equivance class where the remaining
	edges need to be somehow oriented before inference can be done from
	them. Consequently, in applied disciplines, these Directed Acyclic
	Graphs (DAGs) are predominantly constructed manually based on domain
	expertise. Due to being constructed by hand, testing these models is
	vital before making any inference using them. Local testing in these
	models can be done by checking whether the implied conditional
	independences (CIs) by the model hold in the data or not. (Shipley
	2000) also proposed a global test based on combining these local tests.
	Based on these local tests, in the case of continuous or discrete
	variables, we can start by modifying the worst offending test.
\end{abstract}

>>>>

	Causal Discovery that is learning the causal graph from observational
	data is a fundamental problem in causal inference. The problem has been
	extensively studied and many algorithms have been developed to address
	it. However, their adaption in applied fields have been limited,
	possibly due to a lack of confidence in these algorithms stemming from
	them making obvious mistakes, and the difficulties in choosing the
	right algorithm for specific datasets. Moreover, these algorithms can
	usuallly only get us to markov equivance class (MEC) where the
	remaining edges need to be somehow oriented before inference can be
	done from them. Consequently, in applied disciplines, these Directed
	Acyclic Graphs (DAGs) are predominantly constructed manually based on
	domain expertise. Due to being constructed by hand, testing these
	models is vital before making any inference using them. Local testing
	in these models can be done by checking whether the implied conditional
	independences (CIs) by the model hold in the data or not. In the field
	on Structural Equation Models (SEMs), modification indices have been
	used for this purpose where a global fit index is computed relative to
	each possible modification in the model. These modification indices can
	be used to select the appropriate modification backed by expert
	knowledge. In the case of DAGs, we do have global fit index based on
	combining local implied conditional independence tests. Based on this
	test, we can make modifications to our model. This can for example be
	done by using a conditional association measure
\end{abstract}
